Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-21 ms.tex
piddling

\item Unlike stellar heating, heating from SMBH feedback depends on
  the accretion rate, which itself depends on the heating.  Compton heating is generally unimportant compared to stellar
  wind heating for the average SFH, but it can dominate in the case of
  an impulsive star burst (Fig.~\ref{fig:vwSourcesImp}).  Although in
  principle Compton heating is sufficiently high to prevent thermal
  instabilities when acting alone, i.e. $\dot{M}_{C} \lesssim
  \dot{M}_{\rm TI}$ (Fig.~\ref{fig:bh_growth}), SMBH feedback may not
  however be capable of truly stabilizing the flow given its inability
  to respond instantaneously to local changes in the properties of the
  gas.  Kinetic feedback could also be important in determining
  $\dot{M}(M_{\bullet}$) when stellar heating is weak
  ($\S\ref{sec:kinetic}$) but is more challenging to quantify.

@@

%  \item Our calculation of $\Mdot$ agrees well with the one calculated from the Bondi formula. We find that they agree to
 %   within a factor of order unity. This is because in our model the
  %  accretion rate is determined by the flow properties at the
   % stagnation radius, $\rs$, which is within a factor of a few of the
    %Bondi radius $\rb$. Thus, use of the Bondi formula is a
    %good approximation.

>>>>

\item Unlike stellar heating, heating from SMBH feedback depends on
  the accretion rate, which itself depends on the heating.  Compton
  heating is generally unimportant compared to stellar wind heating
  for the average SFH, but it can be significant in the case of an impulsive
  star burst (Fig.~\ref{fig:vwSourcesImp}).  Although in principle
  Compton heating is sufficiently high to prevent thermal
  instabilities when acting alone, i.e. $\dot{M}_{C} \lesssim
  \dot{M}_{\rm TI}$ (Fig.~\ref{fig:bh_growth}), SMBH feedback may not
  be capable of truly stabilizing the flow given its inability
  to respond instantaneously to local changes in the properties of the
  gas.  Kinetic feedback could also be important in determining
  $\dot{M}(M_{\bullet}$) when stellar heating is weak
  ($\S\ref{sec:kinetic}$) but is more challenging to quantify.

@@

  % \item Our calculation of $\Mdot$ agrees well with the one
  %   calculated from the Bondi formula. We find that they agree to
  %   within a factor of order unity. This is because in our model the
  %   accretion rate is determined by the flow properties at the
  %   stagnation radius, $\rs$, which is within a factor of a few of
  %   the
  %   Bondi radius $\rb$. Thus, use of the Bondi formula is a
  %   good approximation.
